### 2022-03-23 src/text/2-package-subsections/stats.tex
[skip ci] Add counts statisitics

>>>>

To perform simple statistical estimations on counts measurements, CountsStatistic classes
encapsulate the aforementioned statistic functions to measure excess counts and estimate the
associated statistical significance, errors and upper limits. They perform maximum likelihood
ratio tests to estimate significance (the square root of the statistic difference) and compute
likelihood profiles to measure errors and upper limits. The following example allows to compute
the Li \& Ma significance~\citep{LiMa} of a set of measurements:
